\documentclass[14pt]{beamer}

\title[Pawpal]{PawPal}
\subtitle[Partners of pethood]{Partners of pethood}
\author[Team 42]{Akshaya Vijay, Tanisha Jain}

\usetheme{CambridgeUS}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}


\begin{frame}
    \frametitle{Overview}
    Our objective is to make an app which will help people find out which dog suits their environment and needs. 
\end{frame}


\begin{frame}
    \frametitle{Technological Stack}
    1. Flutter
    \\*2. Google API
    \\3. MySQl
\end{frame}
   

\begin{frame}
    \frametitle{Description}
    The user would take a personality test which would help us identify the kind of breed they are looking for. 
    \\In the dog-breed-selector test, various questions will be asked. 
    \\Based on the answers suitable dog breeds will be suggested.
\end{frame}


\begin{frame}
    \frametitle{Target Group}
    Pet lovers who want to adopt a dog. 
    
    \begin{block}{Sub-Target Groups}
    \end{block}        

    1. A single working person living alone in a 1BHK apartment, who wants an independent dog who would be a companion and comfort ze.
    \\2. Pet parents who want to provide a home for more dogs.
\end{frame}


\begin{frame}
    \frametitle{Target Group}
    \begin{block}{Sub-Target Groups}
    \end{block}        
    3. A family of 5 with kids under the age of 12, living in a secluded colony, who want a dog to keep watch and provide security. 
    \\*4. A family with a child under the age of 3, who want to adopt a very friendly dog, who would be a good companion for the child.
\end{frame}



\begin{frame}
    \frametitle{Status}
    1. Installed and learning flutter.
    \\*2. Started creating dataset.
    \\*3. Learning about UI/UX.
    \\*4. Learned about mySQL.

\end{frame}


\begin{frame}
    \frametitle{Learnings/ Difficulties faced }
    1. Learned about Google APIs.
    \\*2. Learnt how to create a dataset.
    \\*3. Learned about mySQL. 
    \\*4. Learned how to use Latex. 
    \\*5. Facing difficulties in designing user friendly interface to improve UX. 
    \\*6. Collecting database of dog breeds and pictures.
\end{frame}


\end{document}